Probabilistic Forecast Reconciliation

### 2018-06-19 Presentation/ProbForeRec.tex
fixed mistake in dopt and two other minor changes

  	  \item Collections of time series often characterised by aggregation constraints

@@

  		The true predictive distribution can be recovered via linear reconciliation.  The optimal (but infeasible) mapping is $g(\breve{\bm y})={\bm G}_{opt}\breve{\bm y}+{\bm d}_{opt}$ where $\bm{G}_{opt}={\bm\Omega}^{1/2}{\hat{\bm{\Sigma}}}^{-1/2}$ and ${\bm d}_{opt}={\bm S}{\bm G}_{opt}\left({\bm \mu}-\hat{\bm \mu}\right)$.

@@

  		\item More care must be taken using the energy score.

>>>>

  	  \item Collections of time series are often characterised by aggregation constraints

@@

  		The true predictive distribution can be recovered via linear reconciliation.  The optimal (but infeasible) mapping is $g(\breve{\bm y})={\bm G}_{opt}\breve{\bm y}+{\bm d}_{opt}$ where $\bm{G}_{opt}={\bm\Omega}^{1/2}{\hat{\bm{\Sigma}}}^{-1/2}$ and ${\bm d}_{opt}={\bm G}_{opt}\left({\bm \mu}-\hat{\bm \mu}\right)$.

@@

  		\item Using bottom level series only is a bad idea for energy score.
